### 2018-08-22 Sections/protocols_for_the_quantum_internet.tex
Some new stubs
Telescope fig
Fig update
minor
Dephasing dist metric
Minor telescopy
synthetic telescope array with text filled in

>>>>

%
% Quantum-Enhanced Telescopy
%

\subsection{Quantum-enabled telescopy}\index{Quantum-enhanced telescopy}

\comment{Synthetic aperture}

The light arriving from the distant object is a thermal
state, but the average photon number per mode is much less than 1, therefore higher order terms are negligible. The state that reaches the telescope is therefore in the state

\begin{align}
\ket{\psi_\mathrm{image}} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + e^{i\phi}\ket{1}_A\ket{0}_B).	
\end{align}

\noindent where $\phi$ is the relative phase shift between the two telescope, which depends on the difference in distance travelled. If $\varphi$ can be measured accurately, this can give a precise estimate on the location of the object.

\begin{align}
\phi = \frac{b \sin(\theta)}{\lambda}.
\end{align}

Often the light that arrives will be formed by a mixture of photons from different sources that emit incoherently, and different location give rise to different phase shifts $\varphi$, resulting in a density matrix of the form

\begin{align}
\hat\rho = \frac{1}{2} \left(\begin{matrix}{}
  0 & 0 & 0 & 0 \\
  0 & 1 & \mathcal{V}^* & 0 \\
  0 & \mathcal{V} & 1 & 0 \\
  0 & 0 & 0 & 0
\end{matrix}\right),
\end{align}
where $\mathcal{V}$ is the visibility, reflecting decoherence.

If we interfere the two modes at a 50:50 beam splitter, the photon will exit port 1 with probability
\begin{align}
	p_\mathrm{coin} = \frac{1}{2} (1 + \mathrm{Re}[\mathcal{V}e^{-i\delta}]). 
\end{align}

The problem with implementing the measurement is the difficulty with transporting the single photons state over long distances without incurring loss or additional phase shifts.

Instead of sending a valuable quantum state directly over a noisy quantum channel, instead one can distribute a Bell pair between the two telescope, such as $\ket{01}+\ket{10}$, then we teleport the original quantum state from one telescope to another. The entangled state is known, the preparation can be repeated, and one can use an entanglement distillation protocol to eliminate the phase noise.

Now, we can use the entangled pair directly to measure the visibility, as in Fig.~\ref{fig:telescopy}. We postselect on the measurement results, considering the events where a single photon is observed A and B simultaneously.

The variable delay line is now applied to the entangled state when the photon is sent to A, producing the entangled state 
$\ket{0}_A\ket{1}_B + e^{i\delta}\ket{1}_A\ket{0}_B$.

\begin{align}
\ket{\psi_\mathrm{shared}} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + e^{i\delta}\ket{1}_A\ket{0}_B).	
\end{align}

\begin{figure}[htpb]
\includegraphics[width=0.4\textwidth]{telescopy}
\caption{\comment{To do}.}\label{fig:telescopy}\index{Quantum-enhanced telescopy}	
\end{figure}

 The total probability of seeing a correlation (A1, b1 or A2, b2), conditioned on having one click at each telescope
$\frac{1}{2} (1 + \mathrm{Re}[\mathcal{V}e^{-i\delta}])$
and the total probability of seeing an anticorrelation (A1, B2 or A2, B1) is $\frac{1}{2} (1 - \mathrm{Re}[\mathcal{V}e^{-i\delta}])$\cite{bib:PhysRevLett.109.070503}.
